Analyzing Buildlogs Using Programming by Example

### 2019-06-14 paper/paper.tex
start to properly redo paper bullet points, colored commands for semantic notes

% TODO remove XD
\definecolor{ballblue}{rgb}{0.13, 0.67, 0.8}
\usepackage[color=ballblue]{todonotes}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\section{Introduction}

ci important for sw projects,

broken build stops dev process until its fixed,

shortening fixing time important to increase dev productivity,

to detect underlying failure huge buildlog has to be read, dev has to find relevant information between a lot of lines unimportant for the task,

extracting the dev-relevant information from logs and present only them in a structured way could be key improvement on dev productivity,

traditional: regexes built for exact information extraction

hard to maintain, regex understanding effort, don't generalize / have to be redone when a bulidlog changes / language or build tool is switched,

... our approach ...,

... paper structure ...

@@

\paragraph{Continious integration and analysis of buildlogs}
se research community started to look into buildlogs as CI becomes a vital part of a modern se process

e.g. Seo at al studying the kinds of errors which lead builds to fail at google and their resolvement time \cite{seo2014programmers}

Vasallo et al compared build failure reasons in java open source software and at one industrial company \cite{vassallo2017a-tale}

Beller et al. conducted a large scale empirical analysis of java and ruby buildlogs from travis ci, found that tests are central to CI and main reason for builds to fail \todo{should I mention a key outcome like this or only what they did?}

Vasallo et al. also build a tool to support developers to find reasons for build breaks fast, analyzes and summarizes relevant parts of a buildlog, links to related stack overflow discussions, they found that \begin{quotation}
	dependency breaks and testing failures seem to be easy to understand
\end{quotation} and a good summary highlighting the locality of the issues seems to be an important factor of fixing time \cite{vassallo2018un-break}

relation to our work: we could support this research by enabling easier data extraction from the analyzed buildlogs, most focus on single/few languages with our tool they could more easily cover multiple ones

\paragraph{Information Extraction from semi-structured data using program synthesis}
Le et al. developed FlashExtract as part of the PROSE Framework, tool to synthesize programs based on a few given examples, extract substrings from semi-structured texts, users can extract multiple fields and structure them with hierarchy and sequence, uses inductive synthesis algorithm to synthesize intended program, eliminates the need for the user to understand structure of entire document or to be able to code

we are applying their library to the domain of buildlogs, using programming by example to take away the need to tediously develop and maintain the regular expressions, traditionally used in information extraction

\section{Background}

\paragraph{semi-structured data}
characteristics of semi-structured data (structure irregular, implicit, partial, rapidly evolving) and explaining why this applies to buildlogs, extract information to build a structured layer above the unformed data for efficient data access (for developers here! -> impact on our work with buildlogs) \cite{abiteboul1997querying}

maybe: reference \cite{smith1997information} and explain approach of first structuring into sections / "contexts" before extracting acutal information. but only if we actually do that and not just always parse the whole log.

program synthesis from example, neccessary theoretical stuff,
here all the references to prose theoretical papers \cite{le2014flashextract:}, \cite{polozov2015flashmeta:}, \cite{mitchell1982generalization},

\section{Data collection}
describe process of collecting buildlog files, sampling

\section{Meta-Model}
describe metamodel of data obtainable from buildlogs

\section{Our Tool}

\section{Evaluation}

\section{Conclusion and Future Work}

>>>>

% TODO remove XD
\usepackage{xcolor}
\newcommand{\secfunc}[1]{{\color{magenta}#1}}
\newcommand{\mention}[1]{{\color{cyan}#1}}
\newcommand{\plan}[1]{{\color{purple}#1}}
\newcommand{\bp}[1]{{\color{violet}#1}}
\newcommand{\draft}[1]{{\color{blue}#1}}
\newcommand{\review}[1]{{\color{black}#1}}
\newcommand{\todo}[1]{{\color{orange}#1}}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

\secfunc{section function - secfunc} \\
\mention{things to mention / reference - mention} \\
\plan{what to write here - plan} \\
\bp{actual bullet points - bp} \\
\draft{final text drafty - draft} \\
\review{final text review ready - review} \\
\todo{ToDo - todo} \\

\section{Introduction}
\secfunc{why? what? research questions? purpose? hypothesis? wide $\rightarrow$ narrow}

\bp{build break priority for developers \mention{bart paper}

decreasing the time until a fix therefore improves overall productivity

most time spend: reading very long and verbose buildlog

recovering relevant information from between many uninteresting other lines

support: extract desired information and present in a structured way

usually: tools use handcrafted regular expressions

but: tedious / mentally complicated work, especially when maintenance is needed some months in the future -> reunderstanding old regular expressions is known to be difficult / dreading task for developers

we: take this burden of developers by enabling them to define extraction programs through simply giving examples of the desired extractions

collect a diverse set of buildlogs to  develop a metamodel of the contained information

implement prototype for pbe extractions in buildlogs using the microsoft PROSE library

showed that our tool is capable of extracting various desired informations, shortens development time in comparison to manual regex construction and performs more accurate than other semi-supervised methods

}

@@

\subsection{Continuous Integration}

\plan{more research into CI now, large scale analyses of buildlogs, open source from travis ci and industrial}

\mention{google build analysis}
\plan{google, java and c++, anlyzed frequency and reasons for failures, few error kinds responsible for most failures, dependency errors appear most, most fixed in two build iterations}

\mention{java os vs ing}
\plan{oss and ing for java projects, classfied failures, cluster analysis, similarities: few compilation \& many testing failures, differences: oss mainly unit testing failures, industrial mainly release preparation}

\mention{travistorrent}
\plan{java and ruby builds \& logs from travis ci, manually built parser to extract failure reasons, most builds fail because of tests, number of tests \& kind \& failure rates very dependent on programming language, low failure rates hint at pretested code on CI server}

\plan{our work: support such research through building log file evaluation easier, enable them to cover more languages and build tool kinds}

\subsection{Tool}

\mention{bart}

\mention{icse paper}

\subsection{Information Extraction and Retrieval}

\mention{PROSE fashextract}

\mention{queriying semi structured data}

\mention{sth about IR / paragraph retrieval}

\plan{difference of us to IR (imprecise \& rough)}

\section{Method}
\secfunc{how? when? material? narrow}

\todo{want?: flow of research figure}

\todo{study design vs. study carry out}

\subsection{Data collection}
\plan{describe process of collecting buildlog files, sampling}

\bp{querying ghtorrent and travis api with (insert fancy name for data collection tool) for x buildlogs of each status of the top-watched repositories on github that also use travis ci}

\subsection{Meta-Model}
\bp{through manual examination of y of the buildlogs we collected designed a metamodell  of the contained/extractable/useful/interesting information}

\plan{figure with metamodel}

\plan{explain (shortly? partly?) meta model classes}

\subsection{Our Tool}
\plan{interaction and usage and output of tool, maybe integration possibilities}

\plan{necessary or interesting implementation details}

\section{Results}
\secfunc{hard numbers! answers to research questions, narrow}

\plan{achieved accuracy, samples needed for same accuracy as related tools (travistorrent), aging of learned programs with newer data}

\section{Analysis / Discussion}
\secfunc{interpretation, implication of answers and why does it matter, comparison to previous findings, narrow $\rightarrow$ wide}

\plan{our tool works well for defined cases, limitations of tool/prose/regex usage in general, every x weeks extraction has to be rewritten to keep accuracy, well improved if only y new examples have to be added}

\section{Conclusion and Future Work}
\secfunc{summarize, results again, future research}

\plan{repeat everything and results}

\plan{future}

\bp{make avaliable to other researchers

integrate into travis

\plan{as always} extend evaluation and data collection

use dataset to evaluate against existing approaches

}
